Abstract Data Type Inference

### 2015-03-07 inference.tex
Added references to nature.

For the remainder of this work, we assume each set of executions $E$ comes
equipped with a faithful matching scheme $M$, and abbreviate $H(M,E)$ by $H(E)$.

>>>>

In Section~\ref{sec:nature} we demonstrate faithful matching schemes for the
executions of naturally-occurring concurrent objects, and in
Section~\ref{sec:matching} we demonstrate how to infer faithful matching
schemes. Otherwise, for the remainder of this work, we assume each set of
executions comes equipped with a faithful matching scheme $M$, and abbreviate
$H(M,E)$ by $H(E)$.
